Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-07 paper.tex

% Graphics
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{arrows,positioning,shapes.misc}
\usepackage{graphicx}
\definecolor{lightgrey}{RGB}{170, 170, 170}
\definecolor{darkblue}{RGB}{0, 0, 0}
\definecolor{darkred}{RGB}{170, 0, 0}
\definecolor{darkgreen}{RGB}{0, 110, 0}

@@

The data is then aggregated so that province level flow patterns are emphasized.
\todo{Alvin: Figure must be drawn}
\cref{fig:brussels} provides a diagrammatic representation of the procedure.
First, both origin and destination stations for each data record are spatially aggregated based on provincial administrative boundaries (See \cref{fig:brussels}a).
If an origin or destination station is a located outside of Belgium, it is considered international travel and aggregated in a distinct group (See \cref{fig:brussels}b).
Train stations in major cities are excluded from aggregation so that the volume of flow between provinces and major cities are comparable (See \cref{fig:brussels}c).
The following types of flows are observable from the outcome of aggregation:

>>>>

% Graphics
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{arrows,positioning,shapes.misc}
%\let\subcaption\relax
\usepackage{graphicx}
%\usepackage[caption=false]{subfig}
%\usepackage{caption}
\usepackage{subcaption}
\captionsetup[figure]{labelfont=bf,textfont=bf}
\captionsetup[subfigure]{labelfont=normalfont,textfont=normalfont}
\definecolor{lightgrey}{RGB}{170, 170, 170}
\definecolor{darkblue}{RGB}{0, 0, 0}
\definecolor{darkred}{RGB}{170, 0, 0}
\definecolor{darkgreen}{RGB}{0, 110, 0}

@@

\begin{figure*}
  \centering
  \begin{subfigure}{.475\textwidth}
    \includegraphics[width=8cm]{method-a.pdf}\\
    \subcaption{Spatial aggregation based on provincial administrative boundaries}
    \label{fig:method-a}
  \end{subfigure}%
  \begin{subfigure}{.475\textwidth}
    \includegraphics[width=8cm]{method-b.pdf}\\
    \subcaption{\todo{Alvin: caption to explain what this is}}
    \label{fig:method-b}
  \end{subfigure}%
  \hfill%
  \begin{subfigure}{0.9\textwidth}
    \includegraphics[width=15cm]{method-c.pdf}\\
    \subcaption{Yet another subfigure \todo{Alvin: caption to explain what this is}}
    \label{fig:method-c}
  \end{subfigure}%
  \caption{General caption of the image \todo{Alvin: caption to explain what this is}}
  \label{fig:method}
\end{figure*}

The data is then aggregated so that province level flow patterns are emphasized.
\cref{fig:method} provides a diagrammatic representation of the procedure.
First, both origin and destination stations for each data record are spatially aggregated based on provincial administrative boundaries (see \cref{fig:method-a}).
Train stations in major cities are excluded from aggregation so that the volume of flow between provinces and major cities are comparable (see \cref{fig:method-b}).
If an origin or destination station is a located outside of Belgium, it is considered international travel and aggregated in a distinct group (see \cref{fig:method-c}).
The following types of flows are observable from the outcome of aggregation:
